Simple Wind Models

### 2010-08-02 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5097 ac11df5e-a788-c23b-a8e1-c758c323924d

Although there are several effects that will reduce line emission
relative to the absorption produced by the outflow, our analysis
indicates that detectable line emission should be present for [the
majority] of winds.  One of the principal effects of this emission is
that it modifies the observed absorption profiles (e.g.\
Figure~\ref{fig:noemiss}) which may lead to erroneous conclusions
regarding characteristics of the flow.  {\it Analysis of cool gas outflows
that ignores emission may incorrectly lead to conclusions the gas is
partially covered, has a significantly lower peak optical depth,
and/or that a $v \sim 0 \mkms$ ISM component (perhaps even infall) is
absent.}  Figure~\ref{fig:obs_ew} demonstrates a simple observational
consequence of the line emission: reduced estimates for the absorption
equivalent width \ewabs\ of the flow.  In the case of \ion{Mg}{2},
which has the most affected transitions, the \ewabs\ is reduced by
XX\% for the wind models presented in this paper.

@@

>>>>

Although there are several effects that will reduce line emission
relative to the absorption produced by the outflow, our analysis
indicates that detectable line emission should be present for [the
majority] of winds.  One of the principal effects of this emission is
that it modifies the observed absorption profiles (e.g.\
Figure~\ref{fig:noemiss}) which may lead to erroneous conclusions
regarding characteristics of the flow.  {\it Analysis of cool gas outflows
that ignores emission may incorrectly lead to conclusions the gas is
partially covered, has a significantly lower peak optical depth,
and/or that a $v \sim 0 \mkms$ ISM component (perhaps even infall) is
absent.}  Figure~\ref{fig:obs_ew} demonstrates a simple observational
consequence of the line emission: reduced estimates for the absorption
equivalent width \ewabs\ of the flow.  In the case of \ion{Mg}{2},
which has the most affected transitions, the \ewabs\ is reduced by
$30-50\%$ for the wind models presented in this paper.  This could
yield a systematically lower optical depth for the wind and therefore
a lower total mass and kinetic energy.  Although not apparent in
Figure~\ref{fig:obs_ew}, the effects are most pronounced for wind
scenarios where the peak optical depth occurs near $v = \mkms$.
Simple geometric projection limits the majority of scattered photon emission to
have $v \approx \pm 200 \mkms$ and the absorption profiles
are filled-in primarily at these velocities.  In
Figure~\ref{fig:obs_peaktau}, we plot the observed peak optical depth
for \mgiia\ 
versus the velocity where $\tau = \tau_{pk}$ for the various wind models (i.e.\
$\tau_{pk}$ vs.\ $v_\tau$ from Tables~\ref{tab:line_diag},
\ref{tab:plaw_diag}).   In every one of the models, the intrinsic peak
optical depth exceeds 10 and occasionally exceeds 100.  For the
majority of cases with $v_\tau < -300\mkm$, one observes $\tau_{pk} <
2$ and would infer the wind is not even optically thick!
The results are similar for \mgiib\ although one infers a somewhat
higher column density because of its lower $f\lambda$ value.
In the majority of cases, one would faslely conclude that hte wind
partially covered the source and also estimate a peak optical depth
lower than the intrinsic.

All of these (negative) effects for \ion{Mg}{2} absorption are reduced
for the \ion{Fe}{2} absorption profiles, especially for \feiia.  This
is because a signficant fraction (or even a majority) of the
\ion{Fe}{2} emission is florescent \ion{Fe}{2}* emission at longer
wavelengths which have no effect on the absorption profiles. [word]
Therefore, the \ion{Fe}{2} absorption equivalent widths (\ewabs) more
closely follow the intrinsic value, one derives more accurate peak
optical depths, and the absorption kinematics more faithfully reflect
the motions of the flow.  Regarding the last point, one 
predicts a velocity offset between the peak depth of the \ion{Fe}{2}
centroid and that for \ion{Mg}{2} (Figure~\ref{fig:obs_vtau})
especially when the peak occurs at $v > -400 \mkms$.  One is simply
not sensitive to opacity at $v \sim 0 \mkms$ with the \ion{Mg}{2}
transitions.  This includes gas realted tothe ISM of the galaxy and
also infalling material with modest speeds.  One must take careful
consideration of line emission, therefore,  before drawing robust
conclusions aobut the presence/absence of gas with small velocity
offsets from systemic.

We emphasize that all of these effects are heightened by the
relatively low spectral resolution and S/N characteristic of the data
obtained on $z>0$ star-forming galaxies.  Figure~\ref{fig:obs_lris}a
shows one realization of the \mgiid\ doublet for the fiducial model
convolved with the line-spread-function of the Keck/LRIS spectrometer
(FWHM=250\kms) and an assumed S/N=7 per XX\AA\ pixel.  Both the absorption
and emission profiles are evident, but it is evident that it will be
very difficult to resolve the issues discussed above (e.g.\ partial
covering, incorrect peak optical depth) with these data.  The effects
are even more difficult to predict for spectral stacks, especially
when the systemic redshifts are uncertain by $> 10 \mkms$ (e.g.\ S10).
An example is presnted in Figure~\ref{fig:obs_lris}b, where we have
averaged 200 identical \ion{Mg}{2} profiles from the fiducial model
degraded to a S/N=1\,pix$^{-1}$ and assuming a random redshift error
$\sigma(z) = 40\mkms$.  [Check S10]

[Should galaxies with strong \lya\ emission be expected to show
low-ion emission? Perhaps not if \lya\ is produced by ionizing photons
from SF regions.]

@@

\begin{figure}
\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_peaktau.ps}
\caption{
EW effect
}
\label{fig:obs_peaktau}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_vtau.ps}
\caption{
Velocity offset
}
\label{fig:obs_vtau}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_lris.ps}
\caption{
Velocity offset
}
\label{fig:obs_lris}
\end{figure}
